Demographic Groups with Stronger Biden Support in the Election Race

### 2024-04-03 paper/paper.qmd
update change

ces2022 |> slice_head(n = 10) |>
  kable(booktabs = TRUE, caption = "Brief summary of variables types") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```
After installing `dataverse`[@dataverse], I use `get_dataframe_by_name` to analyze CES. I select four variables that most relevant to our topic, which are `votereg`, `presvote20post`, `educ`, `faminc_new`, `gunown`.  `votereg` represents the voter registration status and only the voter who registered to vote would be considered. Besides, `presvote20post` represents the president that respondents vote in 2020 president election. I only consider the respond of Joe Biden and Donald Trump. `educ` means the education level of the respondents. In addition, `faminc_new` accounts for the family's annual income in 2021 year. `gunown` records the personal gun ownership by asking the respondent to answer whether they or anyone in their household own a gun.
```{r}
#| label: fig-vote
#| fig-cap: The distribution of presidential preferences, by gender, and race
#| echo: false
#| warning: false
#| message: false

>>>>

ces2022 |> slice_head(n = 10) |>
  kable(booktabs = TRUE, caption = "Brief summary of variables types") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```
After installing `dataverse`[@dataverse], I use `get_dataframe_by_name` to analyze CES. I select four variables that most relevant to our topic, which are `votereg`, `presvote20post`, `educ`, `faminc_new`, `gunown`.  `votereg` represents the voter registration status and only the voter who registered to vote would be considered. Besides, `presvote20post` represents the president that respondents vote in 2020 president election. `educ` means the education level of the respondents. In addition, `faminc_new` accounts for the family's annual income in 2021 year. `gunown` records the personal gun ownership by asking the respondent to answer whether they or anyone in their household own a gun. However, for the raw data, there are six different answers, including choosing ,Joe Biden, Donald Trump, Jo Jorgensen, Howie Hawkins, other, and did not vote for President. I only consider the respond of Joe Biden and Donald Trump. Therefore, when I clean the data, I select the group of Joe Biden and Donald Trump. In addition, there are 6 different education level, ranging from no high school, high school graduate, some college, 2-year, 4-year, and post-grad. I care about all of the education level, so I take all of those types into consideration. Moreover, there are 16 ranges of family income and the differences between each range is 10,000. To simiplied the data, I classifed them into 4 different types. For the income group which Less than $10,000,  $10,000 - $19,999, $20,000 - $29,999, and $30,000 - $39,999 are defined as "Low" income group. For those who range from $40,000 to $79,999 can seem as  "Middle" income group.  $80,000 to $199,999 can be considered as "High" income group. For the family earn $200,000 to $500,000 or more is very high income group.
```{r}
#| label: fig-vote
#| fig-cap: The distribution of presidential preferences, by gender, and race
#| echo: false
#| warning: false
#| message: false
